---
title: "p8105_hw1_zq2227.Rmd"
author: "Zixuan Qiu zq2227"
output: github_document
date: "9/20/2023"
---
# Homework1

## Problem 1
Load the moderndive library and the early_january_weather dataset
```{r}
library(moderndive)
```

```{r}
data("early_january_weather")
```


### Write a short description of the dataset;
```{r}
help("early_january_weather")
```

```{r}
summary(early_january_weather)

names(early_january_weather)

str(early_january_weather)

```
```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```
```{r}
mean(early_january_weather$temp)
```
##### This dataset is a hourly meterological data collection that form the  LGA, JFK and EWR on January 2013. This data frame has 15 varibales that is origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed,wind_gust,precip,pressure,visib and time_hour.
 * 15 variables include the 1 character data(origin)that represent the data location. 4 integer variables that represent the time of data collected. 9 numeric variables that represent the meteorological data. And 1 POSIXct time object represent  the specific date and time,  
 * The size of the data set: 358 rows and 15 columns.
 * The mean temperature of the data set is the 39.58212F.
 * Important variables
   * The temperature range:[24.08,57.92]in F. Mean:39.58F. Median: 39.02F.
   * Relative humidity [32.86,100.00 ].  Mean: 65.48%. Median: 61.67%
   * Wind_speed range [0,24.166MPH]. Mean: 8.226MPH. Median: 8.055MPH.  The wind direction are in degrees.
   * Pressure:Sea level pressure in millibars. Median:1022. Mean:1023
   * Visibility in miles [0.120,10.000].  Mean:8.515. Media:10.000  


### Plot 
```{r}
library(tidyverse)
```
```{r}
ggplot(early_january_weather, aes(x =time_hour,y= temp, color= humid)) + geom_point(size=3) +
labs(title= "Temperature and Humidity vs Time hour", y="Temperature(T)", x="Time")
```

#### Description
#### From the graph, it can be concluded that the temperature shows sharp fluctuations in a short  time interval but gradually increases over time. The short-term temperature changes are due to the alternation of day and night, while the overall rise in temperature is due to the warming climate as January progresses. The  relatively humidity is indicated by the color of the points, and the overall relative humidity also gradually increases with time. The humidity in mid-January is noticeably higher than that at the beginning of January.

```{r}
plot1 <-ggplot(early_january_weather, aes(x =time_hour,y= temp, color= humid)) + geom_point(size=3) +
labs(title= "Temperature and Humidity vs Time hour", y="Temperature(T)", x="Time")
```
```{r}
ggsave("problem 1 Temp vs time plot.png", plot=plot1)

```


## Problem 2 
```{r}
norm_samp <- rnorm(10)
#a random sample of size 10 from a standard Normal distribution
norm_samp
```
```{r}
logic_samp <- norm_samp >0
#a logical vector indicating whether elements of the sample are greater than 0
logic_samp
```
```{r}
char_samp<- c("q","a","z","w","s","x","e","d","c","r")
#a character vector of length 10
char_samp
```
```{r}
fact_level <-c("LV1","LV2","LV3")
fact_samp <-sample(fact_level,10,replace = T)
fact_vect <-factor(fact_samp)
#a factor vector of length 10, with 3 different factor “levels”
fact_vect
```
```{r}
p2data <- tibble(norm_samp,logic_samp,char_samp,fact_vect)
#Create the data frame 
p2data
```

### Mean
```{r}
mean_num <- mean(p2data %>% pull(norm_samp), na.rm = TRUE)
mean_num
#mean of norm_samp work
```
```{r}
mean_logic <- mean(p2data %>% pull(logic_samp), na.rm = TRUE)
mean_logic
# mean of logic_samp work 
```
```{r}
mean_char <- mean(p2data %>% pull(char_samp), na.rm = TRUE)
mean_char
#mean of char_samp doesnot work
```
```{r}
mean_factor <- mean(p2data %>% pull(fact_vect), na.rm = TRUE)
mean_factor
#mean fo fact_vect does not work
```
#### Summary: Could take the mean from the numeric or logical vector, However, the mean valuse does not work on the character vector  or factor vector.



